Model Checking Differentially Private Properties

### 2018-01-30 introduction.tex
explain complexity

In order to verify $\dpCTLstar$ properties, we extend the standard
probabilistic model checking algorithms. For Markov chains, the states
satisfying a subformula $\dpriv{\epsilon}{\delta} \phi$ are computed
by a simple variant of the algorithm for Markov chains.
The time complexity of our model checking algorithm is
still polynomial. The logic $\dpCTLstar$ essentially obtains its
expressiveness for free. \bw{double check}
For Markov decision processes, we show that checking whether a state
satisfies $\dpriv{\epsilon}{\delta} \phi$ is undecidable.

>>>>

In order to verify $\dpCTLstar$ properties, we extend the standard
probabilistic model checking algorithms. For Markov chains, the states
satisfying a subformula $\dpriv{\epsilon}{\delta} \phi$ are computed
by a simple variant of the algorithm for Markov chains.
The time complexity of our model checking algorithm is the same as
those of $\CTLstar$ for Markov chains. The logic $\dpCTLstar$ obtains its
expressiveness for free. 
For Markov decision processes, we show that checking whether a state
satisfies $\dpriv{\epsilon}{\delta} \phi$ is undecidable.
